Supplementary Figures 1-x

### 2019-05-15 supplementary_figures/supp1_dataset_description.Rmd
updated supplementary figures

\newpage
# Supplementary Figure `r getFigNb(TRUE)`

```{r cellprops_cor, fig.width=7.5, fig.height=7}
d <- data.frame( dataset=rep(names(SCEs),sapply(SCEs,ncol)), 
                 pct_counts_Mt=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_Mt)),
                 pct_top_50=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_in_top_50_features)),
                 log10_features=unlist(lapply(SCEs,FUN=function(x) x$log10_total_features)))
plot_grid( ggplot(d, aes(x=pct_top_50, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           ggplot(d, aes(x=log10_features, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           labels=LETTERS[1:2], nrow=2 )

ggplot(d, aes(x=log10_features, y=log10_counts, colour=featcount_dist)) + geom_point() + facet_wrap(~dataset, scale="free") + scale_colour_gradient2(limits=c(-0.2,0.2))
```

>>>>

```{r cellprops_cor, fig.width=7, fig.height=8}
d <- data.frame( dataset=rep(names(SCEs),sapply(SCEs,ncol)), 
                 featcount_dist=unlist(lapply(SCEs,FUN=function(x) x$featcount_dist)),
                 log10_counts=unlist(lapply(SCEs,FUN=function(x) x$log10_total_counts)),
                 pct_counts_Mt=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_Mt)),
                 pct_top_50=unlist(lapply(SCEs,FUN=function(x) x$pct_counts_in_top_50_features)),
                 log10_features=unlist(lapply(SCEs,FUN=function(x) x$log10_total_features)))
plot_grid( ggplot(d, aes(x=pct_top_50, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           ggplot(d, aes(x=log10_features, y=pct_counts_Mt)) + geom_point() + facet_wrap(~dataset, scale="free") + geom_density_2d(),
           labels=LETTERS[1:2], nrow=2 )
```
